results

### 2023-02-28 results_work.RMD
updates

###### **Figure 3:** Changes in levels of protein. A) Linear relationship between total RNA (ng x mg) and UBF levels (SD units).

>>>>

###### **Figure 3:** Changes in levels of protein. A) Linear relationship between total RNA (ng x mg) and UBF levels (SD units), with time added as a covariate in the model.

(We must add time as a covariate, as both total RNA and UBF are expected to increase with "time" in this intervention, due to RT. Therefore, adding time as a covariate allows us to model the relationship between RNA and UBF, without variations of time interfering)
